Vragenlijst thesis evaluatie

### 2015-03-01 doc/template/chap-2.tex
sort of games

\section{Conclusion}
The final section of the chapter gives an overview of the important results
of this chapter. This implies that the introductory chapter and the
concluding chapter don't need a conclusion.

>>>>

\subsection{Different kind of games}
De virus has different kind of ways of making his way through the network. The virus can be dropped on a node and than spread itself out to all the neighbours. When a neighbour node is infected it will infect all its neighbours too, so the initial node is back infected. Then their are two options, either the initial node stays infected and does not infect all it neighbours again, or it does. \\
Another propagation method is that the virus works as a token. It will propagate to only one neighbour and continue to spread. 
%waarom kiezen voor een methode
\begin{itemize}
\item A virus can use the mail system to spread itself. This will use then every contact in the contact list so it will spread itself to every neighbour
\item If the virus does not want to get caught it can use the method of a path, infecting only one neighbour.
\item 
\end{itemize}
\section{Conclusion}
The final section of the chapter gives an overview of the important results
of this chapter. This implies that the introductory chapter and the
concluding chapter don't need a conclusion.
